Precise Data Flow Analysis in the Presence of Correlated Method Calls

### 2014-12-13 content/impl.tex
fix ref in intro & mention proofs in supplemental materials

\section{Correlated Calls Analysis}\label{chapter:cca}
The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem. The solution of the IDE problem is converted to a solution of the original IFDS problem. The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.

>>>>

\section{Correlated Calls Analysis}\label{sec:cca}
The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem. The solution of the IDE problem is converted to a solution of the original IFDS problem. The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.

### 2014-12-13 content/intro.tex
fix ref in intro & mention proofs in supplemental materials

We present a formalization of the transformation and prove its correctness
as follows. 
First, we derive an IDE problem that is equivalent to the original IFDS problem,
as described by Reps et al.~\cite{sagiv1996precise}.
Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
Then, we derive a ``Correlated Calls 
IDE Problem'' from the original IFDS problem and show 
that the solution to this problem, when converted to an IFDS result, is more precise
than the original IFDS result.
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
  on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\ref{sec:ccdatastr} and that can be ignored here.
}.

@@

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:ccdatastr} presents the correlated-calls transformation
and a proof of its correctness.
%
The implementation of our approach and preliminary experiments are discussed
in Section~\ref{chapter:eval}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.

>>>>

We present a formalization of the transformation and prove its correctness
as follows. 
First, we derive an IDE problem that is equivalent to the original IFDS problem,
as described by Reps et al.~\cite{sagiv1996precise}.
Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
Then, we derive a ``Correlated Calls 
IDE Problem'' from the original IFDS problem and show 
that the solution to this problem, when converted to an IFDS result, is more precise
than the original IFDS result.
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
  on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\ref{sec:cca} and that can be ignored here.
}.

@@

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:ccdatastr} presents the correlated-calls transformation
and sketches a proof of its correctness%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the supplemental materials that are included with this submission.
}.
%
The implementation of our approach and preliminary experiments are discussed
in Section~\ref{chapter:eval}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.
